Individual Mariculture Modeling Analysis

### 2025-07-10 02_extracting_production_locations.qmd
Proper index of files

source(here("00_dirs.R"))
```

@@

```{r aquaculture-production}
prod <- quantity %>% 
  filter(between(period, 2019, 2023)) %>% 
  group_by(country, Scientific_Name, environment, ISO3_Code, fao_fishing_area) %>% 
  reframe(production = mean(value))

@@

ggplot(prod, aes(x = country, y = production)) +
  geom_point() +
  coord_flip()
```

@@

```{r fix-misalignment}
# filter country level production for all species in non-inland waters where production is greater than 0 tonnes.
mariculture_prod_all <- aquaculture_raw %>% 
  clean_names() %>% 
  select(c(1:7, starts_with("x"))) %>% 
  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
  mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
  filter(year %in% c(2017)) %>% 
  filter(!grepl("Inland waters", fao_major_fishing_area_name)  & 
            !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
                                        "Abalones, winkles, conchs",
                                        "Mussels", 
                                        "Oysters",
                                        "Shrimps, prawns",
                                        "Crabs, sea-spiders",
                                        "Freshwater molluscs",
                                        "Squids, cuttlefishes, octopuses",
                                        "Pearls, mother-of-pearl, shells",
                                        "Miscellaneous aquatic plants",
                                        "Scallops, pectens"),
          !grepl("seaweeds" , asfis_species_name_3),
          !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
  group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) %>% 
  summarise(production = sum(production)) %>% 
  ungroup() %>% 
  mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) %>% 
  group_by(iso3c, country_name, year) %>% 
  nest() %>% 
  mutate(national_production = map(data, ~(sum(.$production)))) %>% 
  unnest(cols = c(data, national_production)) %>% 
  ungroup() %>% 
  filter(production>0) %>% 
  filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
  mutate(model_name = case_when(grepl("rouper", asfis_species_name_2) ~ "general_grouper", 
                              asfis_species_name_2 %in% c("Coho(=Silver) salmon", "Rainbow trout") ~ "general_salmonid",
                              TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) %>% 
  relocate(model_name, .before = asfis_species_name_2) %>% 
  mutate(farm_name = case_when(model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
                                TRUE ~ "General marine fish")) %>% 
  filter(asfis_species_name_2 %in% spp_names) %>% 
  mutate(prop_production = production/national_production)

@@

```{r fix-misalignment}
# filter country level production for all species in non-inland waters where production is greater than 0 tonnes.
mariculture_prod_all <- aquaculture_raw %>% 
  clean_names() %>% 
  select(c(1:7, starts_with("x"))) %>% 
  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
  mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
  filter(year %in% c(2017)) %>% 
  filter(!grepl("Inland waters", fao_major_fishing_area_name)  & 
            !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
                                        "Abalones, winkles, conchs",
                                        "Mussels", 
                                        "Oysters",
                                        "Shrimps, prawns",
                                        "Crabs, sea-spiders",
                                        "Freshwater molluscs",
                                        "Squids, cuttlefishes, octopuses",
                                        "Pearls, mother-of-pearl, shells",
                                        "Miscellaneous aquatic plants",
                                        "Scallops, pectens"),
          !grepl("seaweeds" , asfis_species_name_3),
          !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
  group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) %>% 
  summarise(production = sum(production)) %>% 
  ungroup() %>% 
  mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) %>% 
  group_by(iso3c, country_name, year) %>% 
  nest() %>% 
  mutate(national_production = map(data, ~(sum(.$production)))) %>% 
  unnest(cols = c(data, national_production)) %>% 
  ungroup() %>% 
  filter(production>0) %>% 
  filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
  mutate(model_name = case_when(grepl("rouper", asfis_species_name_2) ~ "general_grouper", 
                              asfis_species_name_2 %in% c("Coho(=Silver) salmon", "Rainbow trout") ~ "general_salmonid",
                              TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) %>% 
  relocate(model_name, .before = asfis_species_name_2) %>% 
  mutate(farm_name = case_when(model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
                                TRUE ~ "General marine fish")) %>% 
  filter(asfis_species_name_2 %in% spp_names) %>% 
  mutate(prop_production = production/national_production)

>>>>

here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
```

@@

```{r aquaculture-production}
production <- quantity %>% 
  filter(between(period, 2017, 2023)) %>% 
  group_by(country, Scientific_Name, environment, ISO3_Code, fao_fishing_area, period) %>% 
  reframe(production = mean(value))

@@

ggplot(production, aes(x = country, y = production)) +
  geom_point() +
  coord_flip()
```

@@

```{r fix-misalignment}
mariculture_prod_all <- production %>% 
  group_by(ISO3_Code, country, period) %>% 
  nest() %>% 
  mutate(national_production = map(data, ~(sum(.$production)))) %>% 
  unnest(cols = c(data, national_production)) %>% 
  ungroup() %>% 
  filter(drop_units(production) > 0) %>% 
  mutate(
    model_name = case_when(
      grepl("Epinephelus|Mycteroperca|Serranidae", Scientific_Name) ~ "grouper", 
      grepl("Oncorhynchus|Salmonidae", Scientific_Name) ~ "general_salmonid", 
      grepl("Salmo salar", Scientific_Name) ~ "atlantic_salmon", 
      grepl("Mytilus|Crassostrea|Ostreidae|Magallana", Scientific_Name) ~ "mussels_oysters",
      grepl("Sparus", Scientific_Name) ~ "bream",       
      grepl("Dicentrarchus", Scientific_Name) ~ "bass",       
      grepl("Ulva|Saccharina|Eucheuma", Scientific_Name) ~ "general_seaweed",       
      grepl("Acipenseridae", Scientific_Name) ~ "sturgeon",
      grepl("Ariidae|Bagridae", Scientific_Name) ~ "catfish",
      grepl("Astacidae|Cambaridae", Scientific_Name) ~ "crayfish",
      grepl("Atherinidae", Scientific_Name) ~ "silversides",
      grepl("Bothidae|Pleuronectidae", Scientific_Name) ~ "flounder",
      grepl("Carangidae", Scientific_Name) ~ "jacks",
      grepl("Cardiidae", Scientific_Name) ~ "cockles",
      grepl("Characidae", Scientific_Name) ~ "tetras",
      grepl("Cyprinidae", Scientific_Name) ~ "minnows",
      grepl("Eleotridae", Scientific_Name) ~ "sleepers",
      grepl("Ex Unionidae|Mytilidae", Scientific_Name) ~ "mussels",
      grepl("Gerreidae", Scientific_Name) ~ "mojarras",
      grepl("Gobiidae", Scientific_Name) ~ "gobies",
      grepl("Lutjanidae", Scientific_Name) ~ "snappers",
      grepl("Monacanthidae", Scientific_Name) ~ "filefish",
      grepl("Mugilidae", Scientific_Name) ~ "mullets",
      grepl("Octopodidae", Scientific_Name) ~ "octopus",
      grepl("Palaemonidae|Penaeus", Scientific_Name) ~ "shrimp",
      grepl("Palinuridae", Scientific_Name) ~ "lobsters",
      grepl("Pectinidae", Scientific_Name) ~ "scallops",
      grepl("Portunidae", Scientific_Name) ~ "crabs",
      grepl("Sciaenidae", Scientific_Name) ~ "drums",
      grepl("Scombridae", Scientific_Name) ~ "mackerels",
      grepl("Scorpaenidae", Scientific_Name) ~ "rockfish",
      grepl("Serranidae", Scientific_Name) ~ "groupers",
      grepl("Soleidae", Scientific_Name) ~ "soles",
      grepl("Sparidae", Scientific_Name) ~ "porgies",
      grepl("Veneridae", Scientific_Name) ~ "clams",
      TRUE ~ NA
  )) %>% 
  relocate(model_name, .before = Scientific_Name) %>% 
  mutate(
    farm_name = case_when(
      model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
      TRUE ~ "General marine fish"
      ),
      Scientific_Name = droplevels(Scientific_Name)
    ) %>% 
  # filter(is.na(model_name)) %>% 
  mutate(prop_production = drop_units(production/national_production)) %>% 
  arrange(prop_production)

write.csv(mariculture_prod_all, "mariculture_production_all.csv")

@@

```{r fix-misalignment-orig}
# filter country level production for all species in non-inland waters where production is greater than 0 tonnes.
mariculture_prod_all <- aquaculture_raw %>% 
  clean_names() %>% 
  select(c(1:7, starts_with("x"))) %>% 
  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
  mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
  filter(year %in% c(2017)) %>% 
  filter(!grepl("Inland waters", fao_major_fishing_area_name)  & 
            !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
                                        "Abalones, winkles, conchs",
                                        "Mussels", 
                                        "Oysters",
                                        "Shrimps, prawns",
                                        "Crabs, sea-spiders",
                                        "Freshwater molluscs",
                                        "Squids, cuttlefishes, octopuses",
                                        "Pearls, mother-of-pearl, shells",
                                        "Miscellaneous aquatic plants",
                                        "Scallops, pectens"),
          !grepl("seaweeds" , asfis_species_name_3),
          !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
  group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) %>% 
  summarise(production = sum(production)) %>% 
  ungroup() %>% 
  mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) %>% 
  group_by(iso3c, country_name, year) %>% 
  nest() %>% 
  mutate(national_production = map(data, ~(sum(.$production)))) %>% 
  unnest(cols = c(data, national_production)) %>% 
  ungroup() %>% 
  filter(production>0) %>% 
  filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
  mutate(model_name = case_when(grepl("rouper", asfis_species_name_2) ~ "general_grouper", 
                              asfis_species_name_2 %in% c("Coho(=Silver) salmon", "Rainbow trout") ~ "general_salmonid",
                              TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) %>% 
  relocate(model_name, .before = asfis_species_name_2) %>% 
  mutate(farm_name = case_when(model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
                                TRUE ~ "General marine fish")) %>% 
  filter(asfis_species_name_2 %in% spp_names) %>% 
  mutate(prop_production = production/national_production)

### 2025-07-10 05_formulating_feeds.qmd
Proper index of files

here("00_model_functions.R") %>% source()
here("00_dirs.R") %>% source()

ingred_inputs_file <- file.path(input_feed_profile_path, "all_ingredients.csv")
feed_input_file <- file.path(input_feed_profile_path, "all_feeds.csv")
overwrite <- F
```

>>>>

here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)

ingred_inputs_file <- file.path(input_feed_profile_path, "all_ingredients.csv")
feed_input_file <- file.path(input_feed_profile_path, "all_feeds.csv")
```

### 2025-07-10 06_run_atlantic_salmon_model.qmd
Proper index of files

library(arrow)
library(sf)
library(dplyr)
library(tidyr)
library(terra)
library(magrittr)
library(furrr)
library(future)
library(tictoc)
library(ggplot2)
library(fs)
library(conflicted)
library(stringr)
library(readxl)
library(units)
library(qs)
library(here)
library(targets)
conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
```

>>>>

library(arrow)
library(sf)
library(dplyr)
library(tidyr)
library(terra)
library(magrittr)
library(furrr)
library(future)
library(tictoc)
library(ggplot2)
library(fs)
library(conflicted)
library(stringr)
library(readxl)
library(units)
library(qs)
library(here)
library(targets)
conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
```
